---
title: "traffic_cleandata"
author: "Thomas Nguyen"
date: "29/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Bug?? summarise convert date to number
Data source: https://discover.data.vic.gov.au/dataset/traffic-signal-volume-data
```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(data.table)

```
Error: std::bad_alloc


```{r}
## Function to read file

read_csvlist <- function(path){
  files <- list.files(path)
  
  df <- map_dfr(str_c(path, "/", files), fread)
  return(df)
}


## Function to get daily value

daily_traffic_summary <- function(data){
 daily_data <-  data  %>%
    select(NB_SCATS_SITE, QT_INTERVAL_COUNT, NB_DETECTOR, QT_VOLUME_24HOUR) %>%
    mutate(date = as_date(QT_INTERVAL_COUNT)) %>%
    group_by(NB_SCATS_SITE, date) %>%
    summarise(traffic_volume = sum(QT_VOLUME_24HOUR))
 
 return(daily_data)
}



## Function to get hourly value
## Suggestion by Dan Simpson
replace_with_zero <- function(x) {
  ifelse(x < 0, yes = 0, no = x)
}

hourly_traffic_cbd_summary <- function(data){
  names(data)[4:99] <- seq(0,24, by = 0.25) 

  hourly_data <- data %>%
    # Trim potential white space
  mutate(NM_REGION = str_trim(NM_REGION)) %>%
    # Get Melboune City data
  filter(NM_REGION %in% c("MC1", "MC2", "MC3")) %>%
  select(1:99) %>% 
    # Replace every values that is negative to 0
  mutate_if(is.numeric, replace_with_zero) %>%
    # Summarise by Scats site
  group_by(NB_SCATS_SITE, QT_INTERVAL_COUNT) %>%
  summarise_if(is.numeric, list(sum)) %>%
  ungroup() %>%
    # Convert the date to longer form
  pivot_longer(4:99, names_to = "hour", values_to = "value" ) %>%
    # Get only the integer number of hour
  mutate(year = year(QT_INTERVAL_COUNT),
         month = month(QT_INTERVAL_COUNT),
         day = day(QT_INTERVAL_COUNT),
         hour = as.numeric(substring(hour,1,2)),
         hourly = make_datetime(year, month,day, hour)) %>%
  group_by(hourly, NB_SCATS_SITE) %>%
  summarise(hourly_value = sum(value)) %>%
  ungroup()
  
  return(hourly_data)
}
```




## Hourly traffic volume for Melbourne city/ Random forest model

Since the data store 15 minutes value in COLUMNS, I need to rotate/ gather them into rows, so I can convert them to hourly data. The problem is, pivot longer couldn't work.
Pivot longer is not an option yet => I was forced to deal with millions rows of data & 100 variables.
What I need to do: Get ALL the negative values out. Group by site and date, then transform all of them into longer form, so all the variables can be converted into hours


```{r}
# WHY HAVEN'T NO ONE WRITTEN SOMETHING LIKE THIS YET?
# Inspired by: https://stackoverflow.com/questions/40724126/replace-negative-values-with-na-for-all-columns

# "if the value is less than 0, put 0, else leave it alone"
replace_with_zero <- function(x) {
  ifelse(x < 0, yes = 0, no = x)
}

```



```{r}
# Bug here, mutate each change everything to numeric will convert to dbl 
# hourly_dat <- VSDATA_20200430 %>% 
#   filter(NM_REGION %in% c("MC1", "MC2", "MC3")) %>%
#   select(1:99) %>% 
#   mutate_each(replace_with_zero) %>%
#   group_by(NB_SCATS_SITE, ) %>%
#   summarise_all(list(sum)) 
# hourly_dat
# 
```
# Read and write hourly traffic for 2019 and 2020


## 2021 data

```{r}
## there was a drop in number of hourly data from 03/2021 till 10/2021
## Number of rows in dataset (using read_csvlist) are the same => Something worng with the hourly_traffic_cbd_summary
hourly_traffic_cbd_202101 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202101/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202102 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202102/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202103 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202103/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202104 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202104/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202105 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202105/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202106 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202106/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202107 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202107/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202108 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202108/")) %>%
  hourly_traffic_cbd_summary()
## Something wrong with 2021-09 data
# hourly_traffic_cbd_202109 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202109/")) %>%
#   hourly_traffic_cbd_summary()
hourly_traffic_cbd_202110 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202110/")) %>%
  hourly_traffic_cbd_summary()
hourly_traffic_cbd_202112 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202112/")) %>%
  hourly_traffic_cbd_summary()


# Use read_csv to read 2021-09 and 2021-11 file
filepath202109 <- here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202109/")
files202109 <- list.files(filepath202109)
  
hourly_traffic_cbd_202109 <- map_dfr(str_c(filepath202109, "/", files202109), read_csv) %>%
    hourly_traffic_cbd_summary()

filepath <- here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202111/")
files <- list.files(filepath)

hourly_traffic_cbd_202111 <- map_dfr(str_c(filepath, "/", files), read_csv) %>%
    hourly_traffic_cbd_summary()

# Combine everything
duplicates(hourly_traffic_cbd_2021)
hourly_traffic_cbd_2021 <- rbind(
      hourly_traffic_cbd_202101,
      hourly_traffic_cbd_202102,
      hourly_traffic_cbd_202103,
      hourly_traffic_cbd_202104,
      hourly_traffic_cbd_202105,
      hourly_traffic_cbd_202106,
      hourly_traffic_cbd_202107,
      hourly_traffic_cbd_202108,
      hourly_traffic_cbd_202109,
      hourly_traffic_cbd_202110,
      hourly_traffic_cbd_202111,
      hourly_traffic_cbd_202112
      )
hourly_traffic_cbd_2021_tsi <- hourly_traffic_cbd_2021 %>% as_tsibble(index = hourly)
```


```{r}
# Lots of lines in 202105 were not read 
# Debug
 # hourly_dat <- traffic_cbd_202105 %>% 
 #   # The problem lies here, there is lots of white space in the values in NM_REGION
 #   # So trim the white space out
 #   mutate(NM_REGION = str_trim(NM_REGION))

```

```{r}
# Debug: Can not read 09/2021 file
# Error: Can't combine `..1$QT_INTERVAL_COUNT` <datetime<UTC>> and `..2$QT_INTERVAL_COUNT` <date>.
# Something is wrong with the date and time (some of the file, QT_INTERVAL_COUNT 
# is registered as date instead of dttm. Fread can't handle it => Use read_csv instead
# 
# filepath <- here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202109/")
# files <- list.files(filepath)
#   
# hourly_traffic_cbd_202109 <- map_dfr(str_c(filepath, "/", files), read_csv) %>%
#     hourly_traffic_cbd_summary()
# 
# hourly_traffic_cbd_202109 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202109/")) %>%

```


### 2020 data

```{r}
# Jan 2020
hourly_traffic_cbd_202001 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202001/")) %>%
  hourly_traffic_cbd_summary()


# Feb 2020
hourly_traffic_cbd_202002 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202002/")) %>%
  hourly_traffic_cbd_summary()

# March 2020
traffic202003 <- read_csvlist(here::here("data/raw-data/raw-traffic/VSDATA_202003"))
hourly_traffic_cbd_202003 <- hourly_traffic_cbd_summary(traffic202003)

# April 2020 data
hourly_traffic_cbd_202004 <- read_csvlist(here::here("data/raw-data/raw-traffic/VSDATA_202004")) %>%
  hourly_traffic_cbd_summary()

### May 2020 data

hourly_traffic_cbd_202005 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202005/")) %>%
  hourly_traffic_cbd_summary()

### Jun 2020 data
hourly_traffic_cbd_202006 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202006/")) %>%
  hourly_traffic_cbd_summary()


### Jul 2020 data
hourly_traffic_cbd_202007 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202007/")) %>%
  hourly_traffic_cbd_summary()


### Aug 2020 data
hourly_traffic_cbd_202008 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202008/")) %>%
  hourly_traffic_cbd_summary()


### Sep 2020 data
hourly_traffic_cbd_202009 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202009/")) %>%
  hourly_traffic_cbd_summary()


### Oct 2020 data
hourly_traffic_cbd_202010 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202010/")) %>%
  hourly_traffic_cbd_summary()


### Nov 2020 data
hourly_traffic_cbd_202011 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202011/")) %>%
  hourly_traffic_cbd_summary()


### Dec 2020 data
hourly_traffic_cbd_202012 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_202012/")) %>%
  hourly_traffic_cbd_summary()

##2020-30-04 data
VSDATA_20200430 <- read_csv(here::here("data/raw-data/raw-traffic/Error files/VSDATA_20200430.csv"))

names(VSDATA_20200430)[4:99] <- seq(0,24, by = 0.25) 

hourly_dat_20200430 <- VSDATA_20200430 %>% 
     # Get Melboune City data
   filter(NM_REGION %in% c("MC1", "MC2", "MC3")) %>%
   select(1:99)  %>%
     # Replace every values that is negative to 0
   mutate_if(is.numeric, replace_with_zero) %>%
     # Summarise by Scats site
   group_by(NB_SCATS_SITE, QT_INTERVAL_COUNT) %>%
   summarise_if(is.numeric, list(sum)) %>%
   ungroup() %>%
     # Convert the date to longer form
   pivot_longer(4:99, names_to = "hour", values_to = "value" ) %>%
     # Get only the integer number of hour
  # fix the date. Change it to 2020-04-30
   mutate(QT_INTERVAL_COUNT = as.POSIXct("2020-04-30 11:00:00"),
          year = year(QT_INTERVAL_COUNT),
         month = month(QT_INTERVAL_COUNT),
         day = day(QT_INTERVAL_COUNT),
         hour = as.numeric(substring(hour,1,2)),
         hourly = make_datetime(year, month,day, hour)) %>%
  group_by(hourly, NB_SCATS_SITE) %>%
  summarise(hourly_value = sum(value)) %>%
  ungroup()
```

```{r}
hourly_traffic_cbd_2020 <- bind_rows(
      hourly_traffic_cbd_202001,
      hourly_traffic_cbd_202002,
      hourly_traffic_cbd_202003,
      hourly_traffic_cbd_202004,
      hourly_dat_20200430,
      hourly_traffic_cbd_202005,
      hourly_traffic_cbd_202006,
      hourly_traffic_cbd_202007,
      hourly_traffic_cbd_202008,
      hourly_traffic_cbd_202009,
      hourly_traffic_cbd_202010,
      hourly_traffic_cbd_202011,
      hourly_traffic_cbd_202012
      )

```


## 2019 data


```{r}
# Error: cannot allocate vector of size 75.9 Mb
hourly_traffic_cbd_20190102 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_201901-02/")) %>%
  hourly_traffic_cbd_summary()

hourly_traffic_cbd_201903 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_201903/")) %>%
  hourly_traffic_cbd_summary()

hourly_traffic_cbd_201904 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_201904/")) %>%
  hourly_traffic_cbd_summary()

hourly_traffic_cbd_20190507 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_201905-07/")) %>%
  hourly_traffic_cbd_summary()

hourly_traffic_cbd_20190810 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_201908-10/")) %>%
  hourly_traffic_cbd_summary()

hourly_traffic_cbd_20191112 <- read_csvlist(here::here("data/raw-data/raw-traffic/Rar-file/VSDATA_201911-12/")) %>%
  hourly_traffic_cbd_summary()

```

```{r}
hourly_traffic_cbd_2019 <- rbind(hourly_traffic_cbd_20190102,
      hourly_traffic_cbd_201903,
      hourly_traffic_cbd_201904,
      hourly_traffic_cbd_20190507,
      hourly_traffic_cbd_20190810,
      hourly_traffic_cbd_20191112)
```

```{r}
saveRDS(hourly_traffic_cbd_2019, file = here::here("data/clean-data/traffic/hourly_traffic_cbd_2019.RDS"))
saveRDS(hourly_traffic_cbd_2020, file = here::here("data/clean-data/traffic/hourly_traffic_cbd_2020.RDS"))
saveRDS(hourly_traffic_cbd_2021, file = here::here("data/clean-data/traffic/hourly_traffic_cbd_2021.RDS"))

# Final Check & further update
hourly_traffic_cbd_2019 <- readRDS(here::here("data/clean-data/traffic/hourly_traffic_cbd_2019.RDS"))
hourly_traffic_cbd_2020 <- readRDS(here::here("data/clean-data/traffic/hourly_traffic_cbd_2020.RDS"))
hourly_traffic_cbd_2021 <- readRDS(here::here("data/clean-data/traffic/hourly_traffic_cbd_2021.RDS"))

## Combine all traffic in 2019-2021
hourly_traffic_cbd <- bind_rows(hourly_traffic_cbd_2019, hourly_traffic_cbd_2020,hourly_traffic_cbd_2021)
saveRDS(hourly_traffic_cbd, file = here::here("data/clean-data/traffic/hourly_traffic_cbd.RDS"))

```

```{r}
hourly_traffic_cbd <- readRDS(here::here("D:/Study/Monash/Semester 4/Air-traffic-Project/data/clean-data/traffic/hourly_traffic_cbd.RDS"))

# Get the hourly volume for all of CBD
hourly_traffic_cbd <- hourly_traffic_cbd %>% 
  group_by(hourly) %>% 
  summarise(cbd_volume = mean(hourly_value))

# Transform to tsibble
hourly_traffic_cbd_tsibble <-  as_tsibble(hourly_traffic_cbd, index = hourly)

# Check for gaps in data
# Gaps are in 2019-12-12, 2020-06-03, 2020-08-07, 2020-09-25
hourly_traffic_cbd_tsibble %>% scan_gaps()

```

