---
title: "Untitled"
author: "Thomas Nguyen"
date: "26/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "Images/", fig.height = 6, fig.width = 8)
```


```{r}
library(tidyverse)
library(naniar)
library(kableExtra)
```

```{r}
# Read in data
train <- read_csv("data/visathon_train_data.csv")
```


```{r}
#  Summary and missing values
train_eda <- train %>% mutate(gender = as.factor(gender),
                 occupation = as.factor(occupation),
                 customer_nw_category = as.factor(customer_nw_category),
                 churn = as.factor(churn)) 

# Summary(train_eda)

train_eda %>% miss_var_summary() %>%
  kable(caption = "Missing variables summary",
        col.names = c("Variable", "Number of missing values", "Percentage of missing values"),
        align = "l") %>%
  kable_styling(bootstrap_options = c("hover", "striped"), latex_options = "hold_position")

```


## Demographic vs Churn


### Gender
```{r}
train_eda %>%
  group_by(gender)%>%
  summarise(count = n()) %>%
  mutate(prop = count/ sum(count)) %>%
  ggplot(aes(x = "", y = prop, fill = gender))+
  geom_col(alpha = 0.8, stat = "identity")+
  geom_text(aes(label = paste(round(prop*100, 1),"%")), size=4, position = position_stack(vjust = 0.5))  + 
  coord_polar("y")+
  scale_y_continuous(labels = scales::percent)+
  theme_minimal()+
  ggtitle("Pie Chart of Gender Rate")+
  xlab("")+
  ylab("")+
  scale_fill_brewer(palette = "Dark2")


```

### Churn Rate

```{r}
train_eda %>%
  group_by(churn)%>%
  summarise(count = n()) %>%
  mutate(prop = count/ sum(count)) %>%
  ggplot(aes(x = "", y = prop, fill = churn))+
  geom_col(alpha = 0.8, stat = "identity")+
  geom_text(aes(label = paste(round(prop*100, 1),"%")), size=4, position = position_stack(vjust = 0.5))  + 
  coord_polar("y")+
  scale_y_continuous(labels = scales::percent)+
  theme_minimal()+
  ggtitle("Pie Chart of Churn rate")+
  xlab("")+
  ylab("")

  

```


```{r}
summary(train_eda)
# Some people have abnormal dependents
# Majority of people are accoutant/ engineer. Very small number of chef => Unbalance
# Nw cat: Low and Medium

# Very high balance in some customer => Log transform

```


### Vintage vs Churn
Because vintage is very right skewed, I use logs
```{r demographic1}
train_eda %>% ggplot(aes(x = log(vintage), fill = churn))+
  geom_density(alpha = 0.4) +
  ggtitle("Logarithms of Vintage vs Churn")+
  xlab("Natural Logarithms of Vintage")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)
  
```

### Age vs Churn

```{r demographic2}
train_eda %>% ggplot(aes(x = age, fill = churn))+
  geom_density(alpha = 0.4)+
  ggtitle("Age vs Churn")+
  xlab("Age")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)

t.test(age ~ churn, data = train_eda)
```


### Dependents vs Churn
```{r demographic3}

train_eda %>% filter(dependents <= 5) %>%
  group_by(dependents, churn)%>%
  summarise(n = n()) %>%
  ggplot(aes(x = as.factor(dependents), y = n, fill = churn))+
  geom_col(alpha = 0.8, position = "fill")+
  geom_text(aes(label=n), position = "fill", vjust = 1.5, size = 5)+
  ggtitle("Dependents vs Churn",
          subtitle = "Proportional Stacked Bar Chart for customers with less than six dependents")+
  xlab("Number of Dependents")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)


```

### Occupication vs Churn
```{r demographic4}
train_eda %>% 
  group_by(occupation, churn)%>%
  summarise(n = n(), 
            sum = sum(n)) %>%
  ggplot(aes(x = as.factor(occupation), y = n, fill = churn))+
  geom_col(alpha = 0.8, position = "fill")+
  geom_text(aes(label=n), position = "fill", vjust = 1.5, size = 5)+
  ggtitle("Occupation vs Churn",
          subtitle = "Proportional Stacked Bar Chart with number of observations")+
  xlab("Occupation")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)

```
### Occupation and Churn
```{r}
train_eda %>% 
  group_by(gender, churn)%>%
  summarise(n = n(), 
            sum = sum(n)) %>%
  ggplot(aes(x = as.factor(gender), y = n, fill = churn))+
  geom_col(alpha = 0.8, position = "fill")+
  geom_text(aes(label=n), position = "fill", vjust = 1.5, size = 5)+
  ggtitle("Gender vs Churn",
          subtitle = "Proportional Stacked Bar Chart with number of observations")+
  xlab("Gender")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)

```
# Bank related Info

```{r bank1}
train_eda %>% 
  group_by(customer_nw_category, churn)%>%
  summarise(n = n(), 
            sum = sum(n)) %>%
  ggplot(aes(x = as.factor(customer_nw_category), y = n, fill = churn))+
  geom_col(alpha = 0.8, position = "fill")+
  geom_text(aes(label=n), position = "fill", vjust = 1.5, size = 5)+
  ggtitle("Customer's Net worth categories vs Churn",
          subtitle = "Proportional Stacked Bar Chart with number of observations")+
  xlab("Networth Categories")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)
```


```{r bank2}
train_eda %>% 
  ggplot(aes(x = days_since_last_transaction, y = churn))+
  geom_boxplot()+
  ggtitle("Days since last transaction vs Churn")+
  xlab("Days since last transaction Categories")+
  ylab("Churn")+
  theme_bw()

```


# Transactional Information
```{r transactional1}
train_log <- train_eda %>% select(churn, current_balance:previous_month_balance) %>% 
  pivot_longer(cols = current_balance:previous_month_balance) %>%
  mutate(log_value = log(value), 
         name = recode(name,
                       "current_balance" = "Balance as of today",
                       "previous_month_end_balance" = "Previous Month End Balance",
                       "average_monthly_balance_prevQ" = "(AMB) in Previous Quarter",
                       "average_monthly_balance_prevQ2" = "(AMB) in previous to previous quarter",
                       "current_month_credit"   = "Total Credit Amount current month",
                       "previous_month_credit" = "Total Credit Amount previous month",
                       "current_month_debit"   = "Total Debit Amount current month",
                       "previous_month_debit"  = "Total Debit Amount previous month",
                       "current_month_balance" = "Average Balance of current month",
                       "previous_month_balance" = "Average Balance of previous month")) 


train_log %>% 
  ggplot(aes(x = value, fill = name))+
  geom_density(alpha = 0.4)+
  ggtitle("Distribution of Transactional Information data")+
  xlab("Value")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Type of Transactional Information")+
  scale_y_continuous(labels = scales::percent)

```


```{r transactional2}  
train_log %>% 
  ggplot(aes(x = log_value, fill = churn))+
  geom_density(alpha = 0.4)+
  facet_wrap(~name)+
  ggtitle("Transactional Information data vs Churn",
          subtitle = "Natural Logarithm transformed")+
  xlab("Natural Logarithm of Value")+
  ylab("Density")+
  theme_bw()+
  labs(fill = "Churn")+
  scale_y_continuous(labels = scales::percent)

# No value = 9


# Depend on current/ previous month debit
```
Most impacts

Customers who close their accounts tend to have higher `current_balance` (Balance as of today), current_month_balance (Average Balance of current month). In contrast, They have lower current_month_debit and previous_month_debit (Total Debit Amount in current month and previous month) than their counterpart. I believe they will have high impact in bui